sensi_an_rotations1. Start of sensitivity analysis for rotations.

### 2018-07-30 inst/documents/sensi_an_rotations1.Rmd
more efficient results storage and add scenario id column

    # add scenario id column onto results
    # this isn't doing anything
    # res$scenario <- i
    df_in_out <- as.data.frame(c(linputs, gens_rot=gens_rot, gens_seq=gens_seq))
    df_in_out$rot_minus_seq <- df_in_out$gens_rot - df_in_out$gens_seq

    # rbind this scenario inputs & results onto previous
    # not a good speed or memory way of doing ... but a start
    df_res_all <- rbind(df_res_all, df_in_out)

@@

# Have a go at running for insecticides with different parameters

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=11, comment=NA}

# set random seed so that results can be reproduced
set.seed(2)
max_gen         <- 500
plot_scenarios  <- FALSE
n_scenarios     <- 10 #000

  df_res_all <- data.frame()

@@

    ## new those below can be different for each insecticide
    linputs$cost <-           runif(n_ins, min=0,   max=0.1) 
    #linputs$cost <-           0 
    linputs$expo_hi <-        runif(n_ins, min=0.4, max=0.9)  #min=0.1, max=0.9
    linputs$male_expo_prop <- runif(1, min=0,   max=1)
    linputs$eff <-            runif(n_ins, min=0.5, max=1) # min=0.3, max=1
    linputs$rr  <-            runif(n_ins, min=0.1, max=0.9)
    linputs$dom_sel <-        runif(n_ins, min=0,   max=1)
    linputs$dom_cos <-        runif(n_ins, min=0,   max=1) 
    linputs$start_freqs <-    runif(n_ins, min=0.005,   max=0.1) #note not log yet

@@

    # add scenario id column onto results
    # this isn't doing anything
    # res$scenario <- i
    df_in_out <- as.data.frame(c(linputs, gens_rot=gens_rot, gens_seq=gens_seq))
    df_in_out$rot_minus_seq <- df_in_out$gens_rot - df_in_out$gens_seq

    # rbind this scenario inputs & results onto previous
    # not a good speed or memory way of doing ... but a start
    df_res_all <- rbind(df_res_all, df_in_out)

@@

>>>>

    # add scenario id column onto results
    df_in_out <- as.data.frame(c(linputs, gens_rot=gens_rot, gens_seq=gens_seq, id=i))
    df_in_out$rot_minus_seq <- df_in_out$gens_rot - df_in_out$gens_seq

    # rbind this scenario inputs & results onto previous
    # not a good speed or memory way of doing ... but a start
    #df_res_all <- rbind(df_res_all, df_in_out)

    #instead set up the dataframe to the required size in scenario1
    if (i==1)
    {
      df_res_all <- data.frame(matrix(NA, ncol=length(names(df_in_out)), nrow=n_scenarios))
      names(df_res_all) <- names(df_in_out)
    }

    #putting results into one row of overall results dataframe
    df_res_all[i,] <- df_in_out

@@

# Have a go at running for insecticides with different parameters
# starting to work ...
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=11, comment=NA}

# set random seed so that results can be reproduced
set.seed(2)
max_gen         <- 500
plot_scenarios  <- FALSE
n_scenarios     <- 100 #1000 #000

  #df_res_all <- data.frame()

@@

    ## new those below can be different for each insecticide
    linputs$cost <-           runif(n_ins, min=0,   max=0.1) 
    #linputs$cost <-           0 
    linputs$expo_hi <-        runif(n_ins, min=0.4, max=0.9)  #min=0.1, max=0.9
    linputs$male_expo_prop <- runif(1, min=0,   max=1)
    linputs$eff <-            runif(n_ins, min=0.5, max=1) # min=0.3, max=1
    linputs$rr  <-            runif(n_ins, min=0.1, max=0.9)
    linputs$dom_sel <-        runif(n_ins, min=0,   max=1)
    linputs$dom_cos <-        runif(n_ins, min=0,   max=1) 
    #DIFFERENT
    linputs$start_freqs <-    runif(n_ins, min=0.0001,   max=0.01) #note not log yet

@@

    # to cope with multiple values per scenario convert them to strings
    linputs2 <- lapply(linputs, function(x) ifelse(length(x)>1,toString(x),x))

    #added scenario id column
    df_in_out <- as.data.frame(c(linputs2, gens_rot=gens_rot, gens_seq=gens_seq, id=i), stringsAsFactors=FALSE)

    df_in_out$rot_minus_seq <- df_in_out$gens_rot - df_in_out$gens_seq

    # rbind this scenario inputs & results onto previous
    # not a good speed or memory way of doing ... but a start
    #df_res_all <- rbind(df_res_all, df_in_out)

    #instead set up the dataframe to the required size in scenario1
    if (i==1)
    {
      df_res_all <- data.frame(matrix(NA, ncol=length(names(df_in_out)), nrow=n_scenarios))
      names(df_res_all) <- names(df_in_out)
    }

    #putting results into one row of overall results dataframe
    df_res_all[i,] <- df_in_out

@@

      # save object containing inputs and results as rda for analysis
      save(df_res_all, file='df_res_all_rot.rda') #paste0(outFolder,'*.rda'))    
    } 
  } #end scenario loop

#to allow plotting of chosen scenarios by re-running them 
#initially didn't work for diff insecticides because the inputs are saved as strings 
#now the strings get converted back to vectors below

scenarios_to_plot <- c(13)

for(scenario in scenarios_to_plot)
{
  #cat(scenario,"\n")
  linputs <- as.list( df_res_all[scenario, 1:15] )

  #converting multiple insecticide inputs back from strings
  #have to ignore the ones that aren't strings
  #linputs2 <- lapply(linputs, function(x) as.numeric(unlist(strsplit(as.character(x),split=", "))))

  #note the space after the comma in split=", "
  linputs <- lapply(linputs, function(x) if (!grepl(",",x)) x else
                                          as.numeric(unlist(strsplit(as.character(x),split=", "))))

  #TESTING changing min_rwr_interval from 5
  linputs$min_rwr_interval <- 0

  # run one scenario (rotation)
  dfres <- do.call(run_rot, linputs)

  ggrot <- rot_plot_resistance(dfres, plot_refuge=FALSE, logy=TRUE, plot=FALSE)

  ggseq <- rot_plot_resistance(dfres, plot_refuge=FALSE, logy=TRUE, plot=FALSE)

  grid.arrange(ggrot, ggseq, ncol=1)
